Constraining Black Hole Growth with High-z Quasar Observations

### 2022-09-26 ms.tex
version0926; me integrating k's 0924 file

%%%%%%%
%    Table. 2 
%%%%%%%
\begin{deluxetable*}{lccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{2} %! fix indexing
\tablewidth{0pt} 
\tablecaption{\blue{Detection Number of Quasars Estimated for Future Surveys} \label{tab:N_detect}} %! reference indexing
\tablehead{
  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
}
\startdata
Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
Wide Euclid & 15000  & $\Muv=-26$ & $154^{+100}_{-38}$  &  $12^{+59}_{-50}$ &   $1^{+4}_{-3}$ & -- & --  \\
\enddata
\tablecomments{
Predicted number of quasars at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey, 
and the bright magnitude with $\Muv=-26$ mag.
In addition, detection limit with 22 mag in the $YJH$ bands is examined for Euclid,
mimicking the effect of quasar selection function.% following \citet{2019A&A...631A..85E}.
}
\end{deluxetable*}

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
for $\fseed=0.1$ (solid) and $0.01$ (dashed).
As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
This result suggests that the information on the seeding process still remains in the low mass regime.
Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
and thus the number density of such massive BHs in the high-mass tail increases.
Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
% BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
the two cases reproduce similar shape of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
%This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
%
%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.

In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
for $\fseed=0.1$ (solid) and $0.01$ (dashed),
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
\end{equation}
%
Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
and $M_\bullet \geq 10^8~\Msun$ (green).
Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
while the mass density barely evolves for the lightest BHs.
At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
Note that the characteristic mass in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
$\fseed=0.1~(0.01)$.
Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
for less massive BHs that keep the information on their initial conditions at birth.

For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}/\Msun<10^8$
%, and $M_\bullet>10^8~\Msun$
obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (dashed-dotted curve).
At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
However, our models predict a larger number of $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
owing to our model prescription that allows BH seed formation earlier on and (modest) super-Eddington episodes.
Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
Upper bounds on the accreted-mass density onto massive BHs (black arrows) prohibits overproduction of low mass BHs at cosmic dawn.
Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants.

@@

Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model.
We divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
The black solid and dashed curve presents the QLF for the unobscured population 
and entire population (including unobscured and obscured quasars), respectively.
The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.

@@

We also show the galaxy UV luminosity function in each panel
along with the fitting functions in a Schechter (dotted) and double power law (dashed-dotted) shape extended to the brighter end
\citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
2021AJ....162...47B, 2022arXiv220712356D,
2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022arXiv220709434N}.
Galaxies at $\Muv\gtrsim -23$ mag dominate quasars in number at all the redshifts and make it 
difficult to identify rare quasars among those faint objects.
Since extrapolated galaxy LFs with a Schechter shape decline quickly with the luminosity increasing,
the abundance of galaxies and quasars becomes comparable around $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
On the other hand, if the bright end of the galaxy LFs are extended with a power law, those critical UV magnitudes shift to 
$\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization.

@@

In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density as a function of redshift for 
$\fseed =0.1$ (solid) and $0.01$ (dashed).
Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
Our theoretical predictions are shown at $z\geq 6$ (thick curves),
while observational results summarized in \cite{2020ApJ...904...89N} are compiled at lower redshifts (thin curves).
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
where $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population
at $z\gtrsim 6$, respectively.
A rapid decay of the luminous quasar abundance at $\Muv<-26$ mag toward higher redshifts is found by 
previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ at $6\lesssim z \lesssim 7$,
consistent with our model prediction where $k_\mathrm{L} \simeq -0.84$.

@@

From the BH growth model described in Section~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in Section~\ref{sec:seed}. 
Adopting the best fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized by $\lambda_0=0.87$ and $\alpha=0.20$ 
(see Section~\ref{sec:fitting_result}).
With these parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.

@@

In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey thin curves).
In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored thick curves),
all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dashed curves),
the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^6~\Msun$ and is 
substantially higher than the mass range for seed BHs.
%ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
%
%If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
%the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
It has been pointed out by \cite{2019ApJ...880...77O} that such simple extrapolation of the growth history for low-$\lambda$ quasars 
does not work properly (see their Figure 10).
% In contrast, the extrapolated growth curves of $z\sim$ 6 super-Eddington BHs are unrealistically steep,
% reaching $<100 ~\Msun$ within several hundred million years.
% This fact indicates short durations of the super-Eddington accretion mode.
For comparison, we show the mass growth tracks assuming continuous Eddington accretion (i.e., $\lambda=1$),
where the extrapolated seed mass is $\Mbh \lesssim 10^2~\Msun$ at $z\sim 30$.
%Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
% \red{Therefore, one may postulate that short durations of super-Eddington accretion lead to the existence of the massive BHs. KI: what do you mean?}
% \blue{It indicates that super-Eddington accretion episodes are required to explain the existence of the massive BHs.}
Based on the BH seeding and growth model we develop,
we reiterate that multiple accretion episodes with different values of $\lambda$ should be taken into account 
to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$,
instead of assuming one single number of the Eddington ratio.

% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
\citet{2021ApJ...907L...1W} discovered the currently known most distant quasar at $z=7.642$ (red diamond in Fig.~\ref{fig:Mevol}).
Assuming continuous Eddington accretion, the extrapolated BH is as massive as $10^{4-6}~\Msun$ at $z= 30$. 
%However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
%taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
%Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
Our best-fit model naturally explains the existence of the most extreme BH,
taking into account the episodical accretion nature of quasars,
%(note extrapolation with the observed $\lambda$ requires an unrealistically high seed mass). 
%including both bursts of accretion and quiescent phases.
%Among the five supermassive BH growth tracks,
%we find one matching this currently known most distant quasar, 
and the consistent growth track among the sub-sample is indicated with the red solid curve 
(with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
This overmassive growth history is realized by the combination of rare halo environments planting a seed BH 
with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.

>>>>

%%%%%%%
%  Table. 2
%%%%%%%
\begin{deluxetable*}{ccccccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{2} %! fix indexing
\tablewidth{0pt}
\tablecaption{Parametric Quasar Luminosity Function}
\tablehead{
  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
  \cline{3-6} \cline{8-11}
  \colhead{Redshift} && \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$ \tilde \beta$}& &
  \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$\tilde \beta$}\\
  & & \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & & & &
  \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & &
}
\startdata
$z\sim 6$  && 46.5 & -23.62 & -1.33 & -2.57    && 89.2 & -23.73 & -1.59 & -2.67 \\
$z\sim 7$  && 6.98 & -23.70 & -1.61 & -2.82   && 12.4 & -23.85 & -1.87 & -2.92 \\
$z\sim 8$  && 1.18 & -23.80 & -1.83 & -3.02   && 1.91 & -23.98 & -2.08 & -3.12 \\
$z\sim 9$  && 0.268 & -23.80 & -1.98 & -3.18  && 0.429& -23.96 & -2.23 & -3.28 \\
$z\sim 10$ && 0.0841 & -23.68 & -2.01 & -3.30 && 0.144 & -23.82 & -2.35 & -3.40 \\
\enddata
\label{tab:QLF_fit}
\tablecomments{Parametric fitting function of both unobscured and intrinsic QLFs at $z=6-10$, produced by the best-fit model with $\fseed=0.01$.
}
\end{deluxetable*}

%%%%%%%
%    Table. 3
%%%%%%%
\begin{deluxetable*}{lccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{3} %! fix indexing
\tablewidth{0pt} 
\tablecaption{\blue{Detection Number of Quasars Estimated for Future Surveys} \label{tab:N_detect}} %! reference indexing
\tablehead{
  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
}
\startdata
Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
Wide Euclid & 15000  & $\Muv=-26$ & $154^{+100}_{-38}$  &  $12^{+59}_{-50}$ &   $1^{+4}_{-3}$ & -- & --  \\
\enddata
\tablecomments{
Predicted number of quasars at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey, 
and the bright magnitude with $\Muv=-26$ mag.
In addition, detection limit with 22 mag in the $YJH$ bands is examined for Euclid,
mimicking the effect of quasar selection function.% following \citet{2019A&A...631A..85E}.
}
\end{deluxetable*}

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
for $\fseed=0.1$ (solid) and $0.01$ (dashed).
As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
This result suggests that the information on the seeding process still remains in the low mass regime.
Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
and thus the number density of such massive BHs in the high-mass tail increases.
Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
% BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
\blue{As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
}%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
%This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
%
%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.

In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
for $\fseed=0.1$ (solid) and $0.01$ (dashed),
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
\end{equation}
%
Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
and $M_\bullet \geq 10^8~\Msun$ (green).
Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
while the mass density barely evolves for the lightest BHs.
At $z\lesssim 7-8$, heavier BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
Namely, the characteristic mass at $z\simeq 6$ in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
$\fseed=0.1~(0.01)$.
Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
which keep the information on their initial conditions at birth.

For comparison, we overlay the BH mass density evolution with $10^6~\Msun<M_{\bullet}<10^8~\Msun$
%, and $M_\bullet>10^8~\Msun$
obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (dashed-dotted curve).
At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
However, our models predict a larger number of $10^{6-8}~\Msun$ BHs emerging at $z\sim 8-10$,
owing to our model prescription that allows BH seed formation earlier on and (modest) super-Eddington episodes.
Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
Upper bounds on the accreted-mass density onto massive BHs (black arrows) prohibits overproduction of low mass BHs at cosmic dawn.
Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants \citep[see also][]{2009ApJ...696.1798T}.

@@

Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model.
We divide the cosmological QLF evolution results into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
The black solid and dashed curves show the QLF for the unobscured population 
and entire population (including unobscured and obscured quasars), respectively.
The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function,
%
\begin{equation}
\Phi(\Muv) = \frac{\Phi^\ast}
{10^{0.4(\tilde \alpha+1)\Delta \Muv} + 10^{0.4(\tilde \beta+1)\Delta \Muv}},
\end{equation}
%
where $\Phi^\ast$ (in units of Gpc$^{-3}$ mag$^{-1}$) is the overall normalization, $\Muv^\ast$ is the characteristic magnitude,
$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ is $\tilde \beta$ are the faint and bright-end power-law slopes, respectively.
In Table~\ref{tab:QLF_fit}, we summarize those parameters of the parametric QLFs at $z=6-10$ for the best-fit models.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.

@@

We also show the galaxy UV luminosity function in each panel
along with the fitting functions in a Schechter (dotted) and double power law (dashed-dotted) shape extended to the brighter end
\citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
2021AJ....162...47B, 2022arXiv220712356D,
2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022arXiv220709434N}.
Galaxies at $\Muv\gtrsim -23$ mag dominate quasars in number at all the redshifts and make it 
difficult to identify rare quasars among those faint objects.
Since the extrapolated galaxy luminosity function with a Schechter shape declines quickly with the luminosity increasing,
the galaxy abundance becomes comparable to that of quasars at $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
On the other hand, if the bright end of the galaxy luminosity function is extended, the critical UV magnitude shifts to
$\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization
(see also \citetalias{2018ApJ...869..150M}, \citealt{2022NatAs...6..850J}).

@@

In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density as a function of redshift for 
$\fseed =0.1$ (solid) and $0.01$ (dashed).
Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
Our theoretical predictions are shown at $z\geq 6$ (thick curves),
while observational results compiled in \cite{2020ApJ...904...89N} are shown at lower redshifts (thin curves).
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
where $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population
at $z\gtrsim 6$, respectively.
A rapid decay of the luminous quasar abundance at $\Muv<-26$ mag toward higher redshifts is found by 
previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$,
consistent with our model prediction \blue{where $k_\mathrm{L} \simeq -0.84$.}

@@

From the BH growth model described in Section~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in Section~\ref{sec:seed}. 
Adopting the best-fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized by $\lambda_0=0.87$ and $\alpha=0.20$ 
(see Section~\ref{sec:fitting_result}).
With those parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.

@@

In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey curves).
In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored solid curves),
all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
Tracing the BH growth curves back with the Eddington ratio observed at $z=6$ (dashed curves),
the extrapolated masses of those massive, sub-Eddington BHs at $z=6$ are as heavy as $\Mbh \gg 10^6~\Msun$ at $z\sim 30$,
which is substantially higher than the mass range for seed BHs.
%ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
%
%If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
%the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
It has been pointed out by \cite{2019ApJ...880...77O} that such simple extrapolation of the growth history for low-$\lambda$ quasars 
does not work properly (see their Figure 10).
% In contrast, the extrapolated growth curves of $z\sim$ 6 super-Eddington BHs are unrealistically steep,
% reaching $<100 ~\Msun$ within several hundred million years.
% This fact indicates short durations of the super-Eddington accretion mode.
For comparison, we show the mass growth tracks assuming continuous Eddington accretion ($\lambda=1$; dashed-dotted curves),
where the extrapolated seed mass is $\Mbh \lesssim 10^2~\Msun$ at $z\sim 30$.
%Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
% \red{Therefore, one may postulate that short durations of super-Eddington accretion lead to the existence of the massive BHs. KI: what do you mean?}
% \blue{It indicates that super-Eddington accretion episodes are required to explain the existence of the massive BHs.}
In conclusion, therefore, multiple accretion episodes with different values of $\lambda$ should be taken into account 
to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$,
instead of assuming one single number of the Eddington ratio.

% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
\citet{2021ApJ...907L...1W} discovered the currently known most distant quasar at $z=7.642$ (red diamond in Fig.~\ref{fig:Mevol}).
Assuming continuous Eddington accretion, the extrapolated BH is as massive as $10^{4-6}~\Msun$ at $z= 30$. 
%However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
%taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
%Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
Our best-fit model naturally explains the existence of the most extreme BH,
taking into account the episodical accretion nature of quasars,
%(note extrapolation with the observed $\lambda$ requires an unrealistically high seed mass). 
%including both bursts of accretion and quiescent phases.
%Among the five supermassive BH growth tracks,
%we find one matching this currently known most distant quasar, 
and the consistent growth track among the sub-sample is indicated with the red solid curve 
(with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
The result demonstrates that the formation of the massive BHs is achieved by the combination of rare halo environments planting a seed BH 
with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.
